figures and calculations for global fisheries management

### 2019-01-11 documents/figs-and-calcs.Rmd
downsample data to fix class imbalance

glm <- glm(formula = CatchShare ~ gdp_center + SpeciesCat, family = "binomial", data = join)
glm

summary(glm)

@@

join_mutate <- left_join(projection_data_mutate, gdp, by = "Country")

@@

glm_broad <- glm(formula = CatchShare ~ gdp_center + MainCat, family = "binomial", data = join_mutate)
glm_broad

summary(glm_broad)

>>>>

itq_fit <- glm(formula = CatchShare ~ gdp_center + SpeciesCatName, family = "binomial", data = join)

summary(itq_fit)

check <- broom::augment(itq_fit)
```

@@

join_mutate <- left_join(projection_data_mutate, gdp, by = "Country") %>% 
  filter(Year == max(Year))

@@

downjoin <- caret::downSample(x = select(join_mutate,-CatchShare),
                              y = factor(join_mutate$CatchShare),
                              yname = "CatchShare")

itq_broad_fit <-
  glm(
    formula = CatchShare ~ gdp_center + MainCat,
    family = "binomial",
    data = downjoin
  )

bayes_itq_broad_fit <-
  rstanarm::stan_glmer(
    formula = CatchShare ~ gdp_center + (1|MainCat),
    family = "binomial",
    data = downjoin,
    cores = 4
  )

summary(itq_broad_fit)

aug_itq_broad_fit <- broom::augment(itq_broad_fit) %>% 
  mutate(pred = predict(itq_broad_fit, type = "response"))

aug_itq_broad_fit %>% 
  ggplot(aes(CatchShare, pred, group = CatchShare)) + 
  geom_boxplot()

aug_itq_broad_fit %>% 
  ggplot(aes(gdp_center, pred, color = MainCat)) + 
  geom_point()

aug_itq_broad_fit %>% 
  ggplot(aes(MainCat, pred)) + 
  geom_boxplot()

plot(bayes_itq_broad_fit)

pps = rstanarm::posterior_predict(bayes_itq_broad_fit) %>% 
  colMeans()

aug_itq_broad_fit <- broom::augment(bayes_itq_broad_fit) %>% 
  mutate(pred = pps)

aug_itq_broad_fit %>% 
  ggplot(aes(CatchShare, pred, group = CatchShare)) + 
  geom_boxplot()

aug_itq_broad_fit %>% 
  ggplot(aes(gdp_center, pred, color = MainCat)) + 
  geom_point()

aug_itq_broad_fit %>% 
  ggplot(aes(MainCat, pred)) + 
  geom_boxplot()
